Model LF

### 2022-12-15 Paper version rmd.Rmd
Commit

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
BEHAVIORAL> lf
TSRANGE 2005 3 2020 1
EQ> lf = theta_00 + theta_01 * TSLAG(ur_ds,1)
COEFF> theta_00 theta_01
STORE> coe(102)

@@

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

@@

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)

COMMENT>
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_shock
if> sens_3 <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> sens_3 > 0

@@

  ##Sensitivites analyse
  prod_shock_sens = TIMESERIES(c(prod),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_disc = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_used = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_ds_shock = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4)
  )
```

@@

#S_modelData$xk_ds_disc = xk_ds

@@

## Baseline Scenario 1

```{r}
shock_lf_model_shock=shock_lf_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs1 <- list(

 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs1
                    )
```

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds

xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1

ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk

ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
```

```{r}
plot(part_bs1, col= "green", main= "Participation rate", ylab= "Participation rate (Ratio)"); lines(part, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2006,3))
```

@@

 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot(wage_ds_t_bs2, col= "green"); lines(wage_ds_t, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(max_dp_bs2, col= "green"); lines(max_dp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

```{r}
plot(wage_gap_bs2, col= "green"); lines(wage_gap, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds

tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

ur_bs3 = Shock_bs3$simulation$ur
```

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

## Baseline Scenario 4

```{r}
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs4 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs4
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

## Baseline Scenario 5

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs56 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs56 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs56
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs56 = Shock_bs56$simulation$max_dp
wage_bs56 = Shock_bs56$simulation$wage
komp_r_bs56 = Shock_bs56$simulation$komp_r
part_bs56 = Shock_bs56$simulation$part
yk_ds_bs56 = Shock_bs56$simulation$yk_ds
pc_ds_bs56 = Shock_bs56$simulation$pc_ds
wage_ds_t_bs56 = Shock_bs56$simulation$wage_ds_t
ur_ds_bs56 = Shock_bs56$simulation$ur_ds
emp_bs56 = Shock_bs56$simulation$emp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds

tilpas_pr_bs56 = Shock_bs56$simulation$tilpas_pr
u_ds_bs56 = Shock_bs56$simulation$u_ds
part_bs56 = Shock_bs56$simulation$part
nben_h_bs56 = Shock_bs56$simulation$nben_h
wage_ds_bs56 = Shock_bs56$simulation$wage_ds
dp_person_bs56 = Shock_bs56$simulation$dp_person
kont_h_ratio_bs56 = Shock_bs56$simulation$kont_h_ratio

nl_g_bs56 = Shock_bs56$simulation$nl_g
unemp_bs56 = Shock_bs56$simulation$unemp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

## Baseline Scenario 5b Sens all

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs5b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 sens_3 = TIMESERIES(sens_3+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs5b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs5b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs5b = Shock_bs5b$simulation$max_dp
wage_bs5b = Shock_bs5b$simulation$wage
komp_r_bs5b = Shock_bs5b$simulation$komp_r
part_bs5b = Shock_bs5b$simulation$part
yk_ds_bs5b = Shock_bs5b$simulation$yk_ds
pc_ds_bs5b = Shock_bs5b$simulation$pc_ds
wage_ds_t_bs5b = Shock_bs5b$simulation$wage_ds_t
ur_ds_bs5b = Shock_bs5b$simulation$ur_ds
emp_bs5b = Shock_bs5b$simulation$emp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds

tilpas_pr_bs5b = Shock_bs5b$simulation$tilpas_pr
u_ds_bs5b = Shock_bs5b$simulation$u_ds
part_bs5b = Shock_bs5b$simulation$part
nben_h_bs5b = Shock_bs5b$simulation$nben_h
wage_ds_bs5b = Shock_bs5b$simulation$wage_ds
dp_person_bs5b = Shock_bs5b$simulation$dp_person
kont_h_ratio_bs5b = Shock_bs5b$simulation$kont_h_ratio

nl_g_bs5b = Shock_bs5b$simulation$nl_g
unemp_bs5b = Shock_bs5b$simulation$unemp
yd_hk_ds_bs5b = Shock_bs5b$simulation$yd_hk_ds
wage_gap1_bs5b = Shock_bs5b$simulation$wage_gap1
wage_gap_bs5b = Shock_bs5b$simulation$wage_gap
prod_bs5b = Shock_bs5b$simulation$prod
```

## Baseline Scenario 7 all but prod and wage

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs7 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7 = Shock_bs7$simulation$max_dp
wage_bs7 = Shock_bs7$simulation$wage
komp_r_bs7 = Shock_bs7$simulation$komp_r
part_bs7 = Shock_bs7$simulation$part
yk_ds_bs7 = Shock_bs7$simulation$yk_ds
pc_ds_bs7 = Shock_bs7$simulation$pc_ds
wage_ds_t_bs7 = Shock_bs7$simulation$wage_ds_t
ur_ds_bs7 = Shock_bs7$simulation$ur_ds
emp_bs7 = Shock_bs7$simulation$emp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds

tilpas_pr_bs7 = Shock_bs7$simulation$tilpas_pr
u_ds_bs7 = Shock_bs7$simulation$u_ds
part_bs7 = Shock_bs7$simulation$part
nben_h_bs7 = Shock_bs7$simulation$nben_h
wage_ds_bs7 = Shock_bs7$simulation$wage_ds
dp_person_bs7 = Shock_bs7$simulation$dp_person
kont_h_ratio_bs7 = Shock_bs7$simulation$kont_h_ratio

nl_g_bs7 = Shock_bs7$simulation$nl_g
unemp_bs7 = Shock_bs7$simulation$unemp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prodk_bs7 = Shock_bs7$simulation$prodk
```

## Baseline Scenario 7b

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs7b <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs7b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs7b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur

y_bs7b = Shock_bs7b$simulation$y
yk_bs7b = Shock_bs7b$simulation$yk

y_yk_bs7= yk_bs7b/y_bs7b
```

## Baseline Scenario 8

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs8 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs8 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs8
                    )
```

>>>>

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

### Remove variables 
lf_remove=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
prod_remove=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

COMMENT> prod-kanal fjernes

COMMENT> 
BEHAVIORAL> prod_ds_endo
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_endo) =  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_endo,1))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_4 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)

COMMENT> 
IDENTITY> prodk
EQ> prodk=prod * (yk/y)
if> prod_remove <= 0

COMMENT>
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_endo
if> sens_3 <= 0 & prod_remove <= 0
IDENTITY> prod_ds
EQ> prod_ds= prod_ds_sens
if> sens_3 > 0 & prod_remove <= 0
IDENTITY> prod_ds
EQ> prod_ds= prodk_ds * (y_ds/yk_ds)
if> sens_3 <= 0 & prod_remove > 0

IDENTITY> prod_remove
EQ> prod_remove = prod_remove*1

COMMENT> LF-kanal fjernes

COMMENT> 
BEHAVIORAL> lf_endo
TSRANGE 2005 3 2020 1
EQ> lf_endo = theta_00 + theta_01 * TSLAG(ur_ds,1)
COEFF> theta_00 theta_01
STORE> coe(102)

IDENTITY> lf
EQ> lf = lf_endo
IF> lf_remove <= 0 
IDENTITY> lf
EQ> lf = lf*1
IF>  lf_remove > 0

IDENTITY> lf_remove
EQ> lf_remove = lf_remove*1

COMMENT> Baseline

@@

@@

@@

  ## Removal variables
   lf_endo = TIMESERIES(c(LF),   
                       START=c(2005,2),FREQ=4),
   prod_ds_endo = TIMESERIES(c(prod_ds),   
                       START=c(2005,2),FREQ=4),
  lf_remove = TIMESERIES(c(lf_remove),   
                       START=c(2005,2),FREQ=4),
  prod_remove = TIMESERIES(c(prod_remove),   
                       START=c(2005,2),FREQ=4),
  ##Sensitivites analyse
  prod_shock_sens = TIMESERIES(c(prod),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_disc = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_used = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_ds_endo = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4)
  )
```

@@

S_modelData$prod_ds_endo = prod_ds

@@

@@

```{r}
lf_remove_model=lf_remove %>% window(start= c(2006,3))
```

@@

 lf_remove = TIMESERIES(lf_remove_model+1 ,START=c(2006,3),  FREQ='Q')

@@

@@

```{r}
prod_remove_model=prod_remove %>% window(start= c(2006,3))
```

@@

 prod_remove = TIMESERIES(prod_remove_model+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
part_bs3 = Shock_bs3$simulation$part
unemp_bs3 = Shock_bs3$simulation$unemp
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
pconk_ds_bs3= Shock_bs3$simulation$pconk_ds
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
unemp_bs3 = Shock_bs3$simulation$unemp
nl_g_bs3 = Shock_bs3$simulation$nl_g
inflation_bs3 = Shock_bs3$simulation$inflation
lf_bs3 = Shock_bs3$simulation$lf
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prodk_ds_bs3 = Shock_bs3$simulation$prodk_ds

xk_ds_bs3 = Shock_bs3$simulation$xk_ds
mk_ds_bs3 = Shock_bs3$simulation$mk_ds

net_balance_bs3 = xk_ds_bs3 - mk_ds_bs3
net_balance_bs3_ratio= (xk_ds_bs3 - mk_ds_bs3)/yk_ds_bs3

ik_bs3 = Shock_bs3$simulation$ik
mk_bs3 = Shock_bs3$simulation$mk

ik_ratio_bs3 = ik_bs3/yk_ds_bs3
mk_ratio_bs3 = mk_bs3/yk_ds_bs3

c_ratio_bs3 = pconk_ds_bs3/yk_ds_bs3
```

### 2022-12-15 max_dp endogen stød.Rmd
Commit

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0
IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_lf_model > 0

@@

```{r}
plot((emp_000-emp_bs1)*1000, col= "red");
```

>>>>

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0

@@

```{r}
plot((unemp_000-unemp_bs1)*1000, col= "red");
```
